### 2023-03-31 reachable-resilience.tex
tryin be less ellyptic, proof needs a bit more robustness checking out tho

\begin{proof}
Taking $\Safe = \{ 0 \}$, $\Bad = S \setminus 0$, it follows the state resilience problem is equivalent
to reachability of $0$. Since reachability of $0$ is undecidable for Reset VASS, we conclude.
\end{proof}

>>>>

\begin{proof}
Consider Reset VASS
in the case $\Safe$ contains only the minimal element %$0$ 
and $\Bad = S \setminus \Safe$, 
it follows the state resilience problem is equivalent 
to the problem of whether $0$ can be visited infinitely often. 
%
% Since reachability of $0$ is undecidable for Reset VASS, we conclude.
Hence the undecidability.
\end{proof}
